---
title: "Practicum 2, part3, Explore and Mine Data"
author: "Zhengyuan Chen & Yi Zhou"
output: html_notebook
---


## 1.Create an R Notebook

Connect to the databases
```{r database_setup, eval = T, warning = F}
library(RMySQL)
# Connect to the MySQL database
db_user <- 'root'
db_password <- 'password'
db_name <- 'p2_db'
db_host <- 'localhost' 
db_port <- 3306

# db connection
mydb <-  dbConnect(RMySQL::MySQL(), user = db_user, password = db_password,
                   dbname = db_name, host = db_host, port = db_port)
```

## 2.use markdown to write a "report" which shows the results of the following analytical queries against your MySQL data warehouse from Part 2

# Analytical Query I: Top five journals with the most articles published in them for the time period. 
```{sql connection=mydb}
SELECT journalTitle, sum(articleNumbers) AS sumOfArticles
FROM journalFact NATURAL JOIN journalDim
GROUP BY journalID
ORDER BY sumOfArticles DESC
LIMIT 5
```

# Analytical Query II: Number of articles per journal per year broken down by quarter.
```{r , eval = T, warning = F}
# Store the result to a dataframe
journal_per_year <- dbGetQuery(mydb, 
   "SELECT journalID, journalTitle, year, quarter, SUM(articleNumbers) AS sumPerQuarter
    FROM JournalFact NATURAL JOIN JournalDim
    WHERE year >= 2012 AND year <= 2015
    GROUP BY journalID, year, quarter")
incidents_by_phase_month
```



```{sql connection=mydb}

```

Disconnect to the databases
```{r}
# Disconnect the MySQL database
dbDisconnect(mydb)
```